### 2007-01-17 Documentation/appendix.tex
*** empty log message ***

A $\gamma=350$ medium gamma $\beta$-beam green-field scenario involving a megaton Water Cerenkov detector can be simulated with the file {\tt
BB\_350.glb}. This file tries to approximate as closely as possible the scenario {\sf Setup III} from
\cite{Burguet-Castell:2005pa}. This reference
should be cited if the file {\tt BB\_350.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt BB\_350.glb}, the following additional files are required: 
\bi
\item {\tt BB350flux.dat} ($\beta$-beam neutrino flux -- $\gamma=350$ )
\item {\tt NeEffMig350.dat} (migration matrix -- $\nu_\mu$)
\item {\tt NeBckgRej350.dat} (migration matrix -- background)
\item {\tt NeDisEff350.dat} (migration matrix -- $\nu_e$)
\item {\tt HeEffMig350.dat} (migration matrix -- $\bar{\nu}_\mu$)
\item {\tt HeBckgRej350.dat} (migration matrix -- background)
\item {\tt HeDisEff350.dat} (migration matrix -- $\bar{\nu}_e$)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
The neutrinos originate from the decays of accelerated isotopes $^{18}$Ne ($\nu_e$) and $^6$He ($\bar{\nu}_e$).
The acceleration factor is $\gamma=350$ for both types of isotopes and $2.2\cdot10^{18}$ $^{18}$Ne decays per
year and $5.8\cdot10^{18}$ $^{6}$He decays per year are assumed. The baseline is L~=~730~km, the
fiducial mass of the detector is $\mathrm{m_{det} = 500 \,kt}$ and 4~years $\nu$-running and 4~years
$\bar{\nu}$-running are assumed. The energy resolution is introduced manually by
six migration matrices (for $\nu_e , \bar{\nu}_e ,\nu_{\mu} ,\bar{\nu}_\mu$, and the background from NC events
for $^{18}$Ne and $^6$He) that describes energy smearing. These migration matrices also already include energy
dependend efficiencies and background rejection factors. They are taken from the appendix of
\cite{Burguet-Castell:2005pa}. The following rules are defined within {\tt BB\_350.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $^{18}$Ne stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $1.0 \, \otimes \, (\nu_e\rightarrow\nu_e)_{\mathrm{CC}}$ & (migration matrix) & 0.025 & $10^{-4}$ \\
 & & & & \\
Background & neglected & (systematic uncertainty dominates) & -- & -- \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^{18}$Ne stored} & & \\ \hline
Signal & $1.0 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & (migration matrix) & 0.025 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$ & (migration matrix) & 0.05 & $10^{-4}$
\\ \hline \hline
\multicolumn{3}{|l|}{Disappearance -- $^6$He stored} & &  \\ \hline
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & (migration matrix) & 0.025 & $10^{-4}$ \\
 & & & & \\
Background & neglected & (systematic uncertainty dominates) & -- & -- \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^6$He stored} & & \\ \hline
Signal & $1.0 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & (migration matrix)  &
0.025 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & (migration matrix) & 0.05 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

@@

A variable neutrino factory scenario can be simulated with the file {\tt NFvar.glb}. The basic version was
used within \cite{Huber:2006wb} and follows the neutrino factory scenarios from \cite{Huber:2002mx}. These
references should be cited if the file {\tt
NFvar.glb} is used for a scientific publication or a talk. For calculations that involve {\tt
NFvar.glb}, the following additional files are required:
\bi
\item {\tt ThresholdEnergies.dat} (list of energies)
\item {\tt CIDthreshold.dat} (list for CID threshold)
\item {\tt MINOSthreshold.dat} (list for MINOS threshold)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
and the values of the following {\sf AEDL}-Variables have to be set:
\bi
\item {\tt emax} (parent energy of the stored muons $\left[\mathrm{km}\right]$)
\item {\tt BASELINE} (experiment baseline $\left[\mathrm{GeV}\right]$)
\ei
The neutrino beam is produced by the decay of muons stored in a storage ring at a parent energy of
$\mathrm{E_\mu =}$~{\tt emax}. The parent energy of the muons can be set in the range
$\mathrm{10\,GeV\lesssim E_\mu\lesssim 80\, GeV}$. The baseline of the scenario is L~=~{\tt BASELINE}. 
Besides these settings the other attributes of {\tt NFvar.glb} are similar to the ones from {\tt
NFstandard.glb}. Only the treatment of the disappearance channels is different. Whereas the CID threshold is
also applied in the disappearance channels of {\tt NFstandard.glb}, this is not the case for the disapperance
channel definition within {\tt NFvar.glb}, where no CID is applied, and a threshold similar to the threshold of
the MINOS experiment \cite{Ables:1995wq} is applied. The following rules are defined within
{\tt NFvar.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^+$-stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.9 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$& 0.025 & $10^{-4}$ \\
 & & & & \\
Background & $1.0\cdot 10^{-5} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.2 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^+$-stored} & & \\ \hline
Signal &  $0.45 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.025 & $10^{-4}$ \\
 & & & & \\
Background &  $5.0\cdot 10^{-6} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ &  $5.0\cdot
10^{-6} \, \otimes \, (\bar{\nu}_\mu \rightarrow\bar{\nu}_\mu)_\mathrm{CC}$ & 0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^-$-stored} & & \\ \hline
Signal &  $0.9 \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\bar{\nu}_e
\rightarrow \bar{\nu}_\mu)_\mathrm{CC}$& 0.025& $10^{-4}$\\
 & & & & \\
Background &  $1.0\cdot 10^{-5} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^-$-stored} & & \\ \hline
Signal & $0.35 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$  & & 0.025& $10^{-4}$\\
 & & & & \\
Background &  $5.0\cdot 10^{-6} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $5.0\cdot 10^{-6} \, \otimes \, (\nu_\mu \rightarrow
\nu_\mu)_\mathrm{CC}$  & 0.2& $10^{-4}$\\ \hline \hline
\end{tabular}
\end{center}

@@

A variable neutrino factory scenario that includes the golden and silver appearance channels can be 
simulated with the file {\tt NF\_GoldSilver.glb}. The basic version was
used within \cite{Huber:2006wb} and the golden channel follows the neutrino factory scenarios from \cite{Huber:2002mx}
and the description of the silver channel follows \cite{Autiero:2003fu}. These
references should be cited if the file {\tt
NFvar\_GoldSilver.glb} is used for a scientific publication or a talk. For calculations that involve {\tt
NFvar\_GoldSilver.glb}, the following additional files are required:
\bi
\item {\tt ThresholdEnergies.dat} (list of energies)
\item {\tt CIDthreshold.dat} (list for CID threshold)
\item {\tt MINOSthreshold.dat} (list for MINOS threshold)
\item {\tt ECCthreshold.dat} (list for ECC threshold)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
and the values of the following {\sf AEDL}-Variables have to be set:
\bi
\item {\tt emax} (parent energy of the stored muons $\left[\mathrm{km}\right]$)
\item {\tt BASELINE} (experiment baseline $\left[\mathrm{GeV}\right]$)
\ei
The beam and golden channel attributes are similar to {\tt NFvar.glb}. The parent energy of the muons can be set
in the range $\mathrm{10\,GeV\lesssim E_\mu\lesssim 80\, GeV}$. The baseline is set by the {\sf
AEDL}-Variable {\tt BASELINE}. For the silver channel, an additional ECC detector with a fiducial mass
$\mathrm{m_{ECC} = 5\,kt}$ is assumed to be located at the same baseline as the MID detector. The energy
resolution of the silver channel is set to $\mathrm{\sigma_e=20\%\cdot E}$. The following additional rule
compared to {\tt NFvar.glb} is introduced in {\tt NF\_GoldSilver.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{$\tau$-Appearance -- $\mu^+$-stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.096 \, \otimes \, (\nu_e \rightarrow \nu_\tau)_\mathrm{CC}$ & & 0.15 & $10^{-4}$ \\
 & & & & \\
Background & $3.1\cdot 10^{-8} \, \otimes \, (\nu_e \rightarrow \nu_e)_\mathrm{CC}$ & $2.0\cdot 10^{-8} \,
\otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$& 0.2 & $10^{-4}$ \\ 
 & $3.7\cdot 10^{-6} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & $1.0\cdot 10^{-3} \,
 \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\tau)_\mathrm{CC}$& 0.2 & $10^{-4}$ \\ 
 & $7.0 \cdot 10^{-7} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $7.0\cdot 10^{-7} \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$& 0.2 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

>>>>

A $\gamma=350$ medium gamma $\beta$-beam scenario involving a megaton Water Cerenkov detector can be simulated with the file {\tt
BB\_350.glb}. This file tries to approximate as closely as possible the scenario {\sf Setup III} from
\cite{Burguet-Castell:2005pa}. This reference
should be cited if the file {\tt BB\_350.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt BB\_350.glb}, the following additional files are required: 
\bi
\item {\tt BB350flux.dat} ($\beta$-beam neutrino flux -- $\gamma=350$ )
\item {\tt NeEffMig350.dat} (migration matrix -- $\nu_\mu$)
\item {\tt NeBckgRej350.dat} (migration matrix -- background)
\item {\tt NeDisEff350.dat} (migration matrix -- $\nu_e$)
\item {\tt HeEffMig350.dat} (migration matrix -- $\bar{\nu}_\mu$)
\item {\tt HeBckgRej350.dat} (migration matrix -- background)
\item {\tt HeDisEff350.dat} (migration matrix -- $\bar{\nu}_e$)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
The neutrinos originate from the decays of accelerated isotopes $^{18}$Ne ($\nu_e$) and $^6$He ($\bar{\nu}_e$).
The acceleration factor is $\gamma=350$ for both types of isotopes and $2.2\cdot10^{18}$ $^{18}$Ne decays per
year and $5.8\cdot10^{18}$ $^{6}$He decays per year are assumed. The ion acceleration would require either a refurbished SPS (with
superconducting magnets) or a more powerful accelerator, such as the
Tevatron or LHC. The baseline is L~=~730~km, the
fiducial mass of the detector is $\mathrm{m_{det} = 500 \,kt}$ and 4~years $\nu$-running and 4~years
$\bar{\nu}$-running are assumed. The energy resolution is introduced manually by
six migration matrices (for $\nu_e , \bar{\nu}_e ,\nu_{\mu} ,\bar{\nu}_\mu$, and the background from NC events
for $^{18}$Ne and $^6$He) that describes energy smearing. These migration matrices also already include energy
dependend efficiencies and background rejection factors. They are taken from the appendix of
\cite{Burguet-Castell:2005pa}. The following rules are defined within {\tt BB\_350.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $^{18}$Ne stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $1.0 \, \otimes \, (\nu_e\rightarrow\nu_e)_{\mathrm{CC}}$ & (migration matrix) & 0.025 & $10^{-4}$ \\
 & & & & \\
Background & neglected & (systematic uncertainty dominates) & -- & -- \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^{18}$Ne stored} & & \\ \hline
Signal & $1.0 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & (migration matrix) & 0.025 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$ & (migration matrix) & 0.05 & $10^{-4}$
\\ \hline \hline
\multicolumn{3}{|l|}{Disappearance -- $^6$He stored} & &  \\ \hline
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & (migration matrix) & 0.025 & $10^{-4}$ \\
 & & & & \\
Background & neglected & (systematic uncertainty dominates) & -- & -- \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance -- $^6$He stored} & & \\ \hline
Signal & $1.0 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & (migration matrix)  &
0.025 & $10^{-4}$ \\
 & & & & \\
Background & $1.0 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & (migration matrix) & 0.05 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

@@

A variable neutrino factory scenario can be simulated with the file {\tt NFvar.glb}. The basic version was
used within \cite{Huber:2006wb} and follows the neutrino factory scenarios from \cite{Huber:2002mx}. These
references should be cited if the file {\tt
NFvar.glb} is used for a scientific publication or a talk. For calculations that involve {\tt
NFvar.glb}, the following additional files are required:
\bi
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
and the values of the following {\sf AEDL}-Variables have to be set:
\bi
\item {\tt emax} (parent energy of the stored muons $\left[\mathrm{km}\right]$)
\item {\tt BASELINE} (experiment baseline $\left[\mathrm{GeV}\right]$)
\ei
The neutrino beam is produced by the decay of muons stored in a storage ring at a parent energy of
$\mathrm{E_\mu =}$~{\tt emax}. The parent energy of the muons can be set in the range
$\mathrm{10\,GeV\lesssim E_\mu\lesssim 80\, GeV}$. The baseline of the scenario is L~=~{\tt BASELINE}. 
Besides these settings the other attributes of {\tt NFvar.glb} are similar to the ones from {\tt
NFstandard.glb}. Only the treatment of the disappearance channels is different. Whereas the CID threshold is
also applied in the disappearance channels of {\tt NFstandard.glb}, this is not the case for the disapperance
channel definition within {\tt NFvar.glb}, where no CID is applied, and a threshold similar to the threshold of
the MINOS experiment \cite{Ables:1995wq} is applied. The following rules are defined within
{\tt NFvar.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^+$-stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.9 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$& 0.025 & $10^{-4}$ \\
 & & & & \\
Background & $1.0\cdot 10^{-5} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.2 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^+$-stored} & & \\ \hline
Signal &  $0.45 \, \otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.025 & $10^{-4}$ \\
 & & & & \\
Background &  $5.0\cdot 10^{-6} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ &  $5.0\cdot
10^{-6} \, \otimes \, (\bar{\nu}_\mu \rightarrow\bar{\nu}_\mu)_\mathrm{CC}$ & 0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Disappearance -- $\mu^-$-stored} & & \\ \hline
Signal &  $0.9 \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & $0.9 \, \otimes \, (\bar{\nu}_e
\rightarrow \bar{\nu}_\mu)_\mathrm{CC}$& 0.025& $10^{-4}$\\
 & & & & \\
Background &  $1.0\cdot 10^{-5} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.2& $10^{-4}$\\ \hline \hline
\multicolumn{3}{|l|}{Appearance -- $\mu^-$-stored} & & \\ \hline
Signal & $0.35 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$  & & 0.025& $10^{-4}$\\
 & & & & \\
Background &  $5.0\cdot 10^{-6} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $5.0\cdot 10^{-6} \, \otimes \, (\nu_\mu \rightarrow
\nu_\mu)_\mathrm{CC}$  & 0.2& $10^{-4}$\\ \hline \hline
\end{tabular}
\end{center}

@@

A variable neutrino factory scenario that includes the golden and silver appearance channels can be 
simulated with the file {\tt NF\_GoldSilver.glb}. The basic version was
used within \cite{Huber:2006wb} and the golden channel follows the neutrino factory scenarios from \cite{Huber:2002mx}
and the description of the silver channel follows \cite{Autiero:2003fu}. These
references should be cited if the file {\tt
NFvar\_GoldSilver.glb} is used for a scientific publication or a talk. For calculations that involve {\tt
NFvar\_GoldSilver.glb}, the following additional files are required:
\bi
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
and the values of the following {\sf AEDL}-Variables have to be set:
\bi
\item {\tt emax} (parent energy of the stored muons $\left[\mathrm{km}\right]$)
\item {\tt BASELINE} (experiment baseline $\left[\mathrm{GeV}\right]$)
\ei
The beam and golden channel attributes are similar to {\tt NFvar.glb}. The parent energy of the muons can be set
in the range $\mathrm{10\,GeV\lesssim E_\mu\lesssim 80\, GeV}$. The baseline is set by the {\sf
AEDL}-Variable {\tt BASELINE}. For the silver channel, an additional ECC detector with a fiducial mass
$\mathrm{m_{ECC} = 5\,kt}$ is assumed to be located at the same baseline as the MID detector. The energy
resolution of the silver channel is set to $\mathrm{\sigma_e=20\%\cdot E}$. The following additional rule
compared to {\tt NFvar.glb} is introduced in {\tt NF\_GoldSilver.glb}:
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{$\tau$-Appearance -- $\mu^+$-stored} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.096 \, \otimes \, (\nu_e \rightarrow \nu_\tau)_\mathrm{CC}$ & & 0.15 & $10^{-4}$ \\
 & & & & \\
Background & $3.1\cdot 10^{-8} \, \otimes \, (\nu_e \rightarrow \nu_e)_\mathrm{CC}$ & $2.0\cdot 10^{-8} \,
\otimes \, (\nu_e \rightarrow \nu_\mu)_\mathrm{CC}$& 0.2 & $10^{-4}$ \\ 
 & $3.7\cdot 10^{-6} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & $1.0\cdot 10^{-3} \,
 \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\tau)_\mathrm{CC}$& 0.2 & $10^{-4}$ \\ 
 & $7.0 \cdot 10^{-7} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $7.0\cdot 10^{-7} \, \otimes \, (\nu_e \rightarrow \nu_x)_\mathrm{NC}$& 0.2 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

### 2007-01-17 Documentation/part1.tex
*** empty log message ***

medium $\gamma$ & {\tt BB\_350.glb} & $\gamma=350$ frogreen field scenario, 4~yr $\nu$- and
4~yr $\bar{\nu}$-running & \cite{Burguet-Castell:2005pa} \\[0.2cm]

@@

 \hspace*{0.5cm} /* Add oscillation parameter priors */ \\
  \hspace*{0.5cm}  for(i=0;i<6;i++) \\
  \hspace*{0.5cm} if(glbGetProjectionFlag(p,i)==GLB\_FREE) \\
  \hspace*{0.5cm} \{ \\
  \hspace*{1cm} fitvalue=glbGetOscParams(in,i); \\
  \hspace*{1cm} centralvalue=glbGetOscParams(central\_values,i); \\
  \hspace*{1cm} inputerror=glbGetOscParams(input\_errors,i); \\
  \hspace*{1cm} if(inputerror>1e-12) 
  \hspace*{1cm} \{ \\
  \hspace*{1.5cm} if(i==GLB\_THETA\_12) /* Prior on $\sin^2 \theta_{12}$ */ \\ 
\hspace*{2.0cm} pv+=square((square(sin(startvalue))-fitvalue)/inputerror);\\ 
  \hspace*{1.5cm} else \\ 
  \hspace*{2.0cm}  pv+=square((startvalue-fitvalue)/inputerror); \\
  \hspace*{1cm} \} \\
  \hspace*{0.5cm} \}

>>>>

medium $\gamma$ & {\tt BB\_350.glb} & $\gamma=350$, refurbished SPS scenario, 4~yr $\nu$- and
4~yr $\bar{\nu}$-running & \cite{Burguet-Castell:2005pa} \\[0.2cm]

@@

 \hspace*{0.5cm} /* Add oscillation parameter priors */ \\
  \hspace*{0.5cm}  for(i=0;i<6;i++) \\
  \hspace*{0.5cm} if(glbGetProjectionFlag(p,i)==GLB\_FREE) \\
  \hspace*{0.5cm} \{ \\
  \hspace*{1cm} fitvalue=glbGetOscParams(in,i); \\
  \hspace*{1cm} centralvalue=glbGetOscParams(central\_values,i); \\
  \hspace*{1cm} inputerror=glbGetOscParams(input\_errors,i); \\
  \hspace*{1cm} if(inputerror>1e-12) 
  \hspace*{1cm} \{ \\
  \hspace*{1.5cm} if(i==GLB\_THETA\_12) /* Prior on $\sin^2 \theta_{12}$ */ \\ 
\hspace*{2.0cm} pv+=square((startvalue-square(sin(fitvalue)))/inputerror);\\ 
  \hspace*{1.5cm} else \\ 
  \hspace*{2.0cm}  pv+=square((startvalue-fitvalue)/inputerror); \\
  \hspace*{1cm} \} \\
  \hspace*{0.5cm} \}
